Frozen Civil Conflicts

### 2024-01-29 paper.qmd
Replace json-based model runs in manuscript

theme_set(theme_tufte(base_family = "TeX Gyre Pagella", base_size = 10))
```

@@

@@

```{r}
#| fig.cap: Posterior estimates for \delta from a single variate probit model
fit <- readRDS("./posteriors/frozen-bin-all/fit.rds")

@@

```{r}
#| fig.cap: Average marginal effects for the three treatment conditions on the predicted probability of a frozen conflict onset.[^ame]

ame <- fit$draws("ame", format = "df") |>
    select(matches("ame")) |>
    pivot_longer(everything(), names_to = "variable")

>>>>

theme_set(theme_tufte(base_family = "TeX Gyre Pagella", base_size = 10))

design <- readRDS("./data/models/design.rds")
```

@@

Why do external states intervene in civil conflicts? To further their national interests. Interveners face constraints, strategic decisions over limited resources, as well as from other interveners (ex: Anderson 2019)

@@

```{r}
#| fig.cap: Posterior estimates for \delta from a single variate probit model
main_model <- filter(design, outcome == "frozen", treatment == "bin", episodes == "all",
                     censored == "with_censored") |> pull(id)

fit <- sprintf("posteriors/data_%s/fit.rds", main_model) |>  readRDS()

@@

```{r}
#| fig.cap: Average marginal effects for the three treatment conditions on the predicted probability of a frozen conflict onset.[^ame]
ame <- fit$draws("ame", format = "df") |>
    select(matches("ame")) |>
    pivot_longer(everything(), names_to = "variable")
